
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Issam Fradi} \\ \vspace{1pt}
    215 Jardin de l'Arche, 92000 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +33 (0) 7 82 80 62 61  ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mohamed-issam.fradi@dauphine.eu}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/issam-fradi-77577b179/}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/IssamFradii}}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Paris-Dauphine University - PSL, Paris}{2023 -- 2024}
      {MSc 272 in Financial Engineering and Economics, with Honours}{}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant courses}: Stochastic Calculus, Econometrics, Derivatives, VBA, Python, Pricing and Arbitrage, Data Management.}
        \resumeItem{\textbf{Financial Analysis Project}: Estimated and tested the Fama-French Five-Factor model using Python.}
        \resumeItem{\textbf{Econometrics Project}: Conducted a time series analysis on the correlation between the DAX index and inflation using R Studio.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Paris-Dauphine University - PSL, Paris}{2020 -- 2023}
      {Bachelor’s Degree in Economics and Financial Engineering, with Honours}{}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant courses}: Portfolio Management, Maths for Economics and Finance, Python, VBA, Econometrics.}
        \resumeItem{\textbf{Portfolio Management Project}: Developed a VBA model to analyze market index performance and risk via maximum drawdown calculations.}
      \resumeItemListEnd

    \resumeSubheading
      {Lycée Pilote Sousse, Tunisia}{2017 -- 2020}
      {Baccalaureate in Science, Mathematics Major, Highest Honours}{}
  
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCES}
  \resumeSubHeadingListStart

    \resumeSubheading
  {Aktionnaire}{November 2023 -- Present}
  {Brand Ambassador}{Paris, France}
  \resumeItemListStart
    \resumeItem{Representing Aktionnaire’s mission to demystify finance and investment topics to a young audience through engaging and educational content.}
    \resumeItem{Leveraging various digital platforms, including Instagram and newsletters, to communicate economic trends and insights in an accessible manner.}
    \resumeItem{Collaborating with a dynamic team to create and distribute content that resonates with a youth audience, contributing to a growing follower base.}
  \resumeItemListEnd
    \resumeSubheading
      {KRYPTOSPHERE® Dauphine}{October 2023 -- Present}
      {Sponsorship Associate}{Paris, France}
      \resumeItemListStart
        \resumeItem{Engaging with corporate sponsors to secure funding and support for a trading competition event in collaboration with KRYPTOSPHERE® ESSEC.}
        \resumeItem{Developing and maintain relationships with key industry players, enhancing the organization's network and visibility.}
        \resumeItem{Analyzing market trends to identify potential sponsorship opportunities and present strategic recommendations to the team.}
      \resumeItemListEnd

    \resumeSubheading
  {La Belle Vie}{October 2023 -- Present}
  {Team Leader - Cold Zone}{Paris, France}
  \resumeItemListStart
    \resumeItem{Overseeing a team of 10+ employees, coordinating schedules and delegating tasks to ensure efficient operation and customer satisfaction.}
    \resumeItem{Maintaining high levels of team morale and performance through effective leadership and clear communication.}
    \resumeItem{Managing inventory and supplier relationships to ensure the seamless availability of products in the cold zone.}
  \resumeItemListEnd


    
      
    

  \resumeSubHeadingListEnd

%----------LANGUAGE AND IT SKILLS------------
\section{ACTIVITIES \& COMPETENCIES}
\begin{itemize}[leftmargin=0.15in , label={}]
    \small{\item{
     \textbf{Languages:} French (Bilingual), English (Fluent), Arabic (Native). \\
     \vspace{5pt}
     \textbf{Competencies:} MS Office Suite (Excel, PowerPoint, etc.), Bloomberg. \\
     \vspace{5pt}
     \textbf{Programming Languages:} VBA (Advanced), Python (Advanced), R studio (Intermediate), SQL, HTML. \\
     \vspace{5pt}
     \textbf{Certificates:} Completion of Finance Accelerator - AmplifyMe x Morgan Stanley, Bloomberg Market Concepts (BMC) - Bloomberg for Education.
    }}
\end{itemize}





\end{document}
